New Insights on the Role of Context in the Perception of a Human-like Robot

### 2015-03-12 main.tex
[wip] Improve the presentation of conditions and stimuli

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}
\usepackage{xspace}

@@

@@

\subsubsection{Video Stimuli}

>>>>

\usepackage{graphicx} 
\usepackage{subfigure}
\usepackage{paralist}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{url}
\usepackage{xspace}
\usepackage{booktabs}

\usepackage{tikz}
\usetikzlibrary{decorations.pathreplacing}
\newcommand{\tikzmark}[1]{\tikz[overlay,remember picture] \node (#1) {};}

@@

\section{Experimental Design}

\subsection{Conditions}

\begin{figure}
    \centering
    \small

    \tikzmark{top}

    \tikzmark{left}
    \begin{tabular}{l|p{2.5cm}|p{2.5cm}}
        & \tikzmark{top1} Shallow cognitive context & Deep cognitive \tikzmark{top2} context  \\
        \hline
        \tikzmark{left1} Robot & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''} \\
        \hline
        \tikzmark{left2} Human & {\bf A}: \emph{``Pick the brown toy''} & {\bf A}: \emph{``Pick your favorite toy''} \\ 
                               & {\bf B}: \emph{``Point at the noise''} & {\bf B}: \emph{``Point at the crying baby''}\tikzmark{bottom} \\
        \end{tabular}

    % draw the over- and side-braces
    \begin{tikzpicture}[overlay, remember picture]

        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
            (top -| top1.west) --  (top -| top2.east) node[midway, above=0.5em] {\scriptsize between subjects};

        \draw [decoration={brace,amplitude=0.5em},decorate,thick]
            (left |- bottom) --  (left |- left1.north) node[midway,above=3em,left=1em,rotate=90] {\scriptsize within subject};
    \end{tikzpicture}
    %%%

    \caption{\small 2x2 design: the \emph{robot} vs \emph{human} condition is within
        subject, while the \emph{shallow cognitive context} vs \emph{deep
        cognitive context} is between subject. Two stimuli (\emph{``toys''}
        scene, {\bf A}, and \emph{``noise''} scene, {\bf B})
        were shown to the participants, introduced by brief verbal commands, reproduced
        here. While visually identical (see screenshots on
        figure~\ref{fig:stimuli}), the stimuli were introduced with different
        commands in the two conditions \emph{shallow} and \emph{deep cognitive
        context}.}

    \label{}
\end{figure}

\subsection{Video Stimuli}

\begin{figure}
    \centering
    \subfigure[\emph{Toys} scene, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-toys}
    }
    \subfigure[\emph{Toys} scene, human condition]{
        \includegraphics[height=3cm]{stimulus-human-toys}
    }

    \subfigure[\emph{Noise} scene, robot condition]{
        \includegraphics[height=3cm]{stimulus-robot-noise}
    }
    \subfigure[\emph{Noise} scene, human condition]{
        \includegraphics[height=3cm]{stimulus-human-noise}
    }

    \caption{\small Screenshots of the 2x2 stimuli. Note that the images above have been
    slightly cropped: the original video are framed so that the agent (robot or
    human) always remains entirely visible.}
    \label{fig:stimuli}
\end{figure}

@@
